%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{graphicx}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}
\newcommand{\resumeItemSimple}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\newcommand{\resumeSubItemSimple}[1]{\resumeItemSimple{#1}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand\sbullet[1][.7]{\mathbin{\vcenter{\hbox{\hspace{3pt}\scalebox{#1}{$\bullet$}\hspace{3pt}}}}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Kyle Chadha}} & Email: \href{mailto:kyle.chadha@gmail.com}{kyle.chadha@gmail.com}\\
  \href{http://www.kylechadha.com/}{http://www.kylechadha.com} & Mobile: +1-858-231-0672 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California at Berkeley}{Berkeley, CA}
      {B.S. from the Haas School of Business}{2005 - 2009}
      \resumeItemListStart
        \resumeItemSimple{GPA: 3.7/4.0; Recipient of the Management of Engineering and Innovation Certificate}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Thomson Reuters (now Refinitiv)}{New York, NY}
      {Software Engineer}{Jan 2016 - Dec 2019}
      \resumeItemListStart
        \resumeItem{Tensorflow}
          {TensorFlow is an open source software library for numerical computation using data flow graphs; primarily used for training deep learning models. Worked on APIs and performance for training models on Tensor Processing Units (TPU).}
        \resumeItem{Apache Beam}
          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines, as well as a set of language-specific SDKs for constructing pipelines and runners.}
      \resumeItemListEnd

    \resumeSubheading
      {BuzzFeed}{New York, NY}
      {Frontend Engineer}{Mar 2014 - Jan 2015}
      \resumeItemListStart
        \resumeItem{Notifications}
          {Service for sending email, push and in-app notifications. Involved in features such as delivery time optimization, tracking, queuing and A/B testing. Built an internal app to run batch campaigns for marketing etc.}
        \resumeItem{Nostos}
          {Bulk data processing and injection service from Hadoop to Cassandra and provides a thin REST layer on top for serving offline computed data online.}
        \resumeItem{Workflows}
          {Dataduct an open source workflow framework to create and manage data pipelines leveraging reusables patterns to expedite developer productivity.}
        \resumeItem{Data Collection}
          {Designed the internal survey and crowd sourcing platform which allowed for creating various tasks for crowd sourcing or embedding surveys across the Coursera platform.}
        \resumeItem{Dev Environment}
          {Analytics environment based on docker and AWS, standardized the python and R dependencies. Wrote the core libraries that are shared by all data scientists.}
        \resumeItem{Data Warehousing}
          {Setup, schema design and management of Amazon Redshift. Built an internal app for access to the data using a web interface. Dataduct integration for daily ETL injection into Redshift.}
        \resumeItem{Recommendations}
          {Core service for all recommendation systems at Coursera, currently used on the homepage and throughout the content discovery process. Worked on both offline training and online serving.}
        \resumeItem{Content Discovery}
          {Improved content discovery by building a new onboarding experience on coursera. Using this to personalize the search and browse experience. Also worked on ranking and indexing improvements.}
        \resumeItem{Course Dashboards}
          {Instructor dashboards and learner surveying tools, which helped instructors run their class better by providing data on Assignments and Learner Activity.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Socify \& AdaptForce}{Los Angeles, CA}
      {CTO and Co-Founder}{Apr 2013 – Mar 2014}
      \resumeItemListStart
        \resumeItemSimple
          {Led the product design and development process for two early stage entrepreneurial projects [and fell in love with software development...]}
        \resumeItemSimple
          {Responsible for day to day management of the outsourced dev team, product design, and operations}
      \resumeItemListEnd

    \resumeSubheading
      {Clinton Foundation}{Kigali, Rwanda}
      {Senior Associate}{Jan 2013 - Jul 2013}
      \resumeItemListStart
        \resumeItemSimple
          {Advised the Rwandan government on the integration of analytics into their resource tracking and decision systems}
        \resumeItemSimple
          {Performed a number of high level analyses to deepen the government’s understanding of the flow of funding into the country and quantify the true cost of various coverage options}
      \resumeItemListEnd

    \resumeSubheading
      {ZS Associates}{Los Angeles, CA}
      {Associate Consultant (2012), Associate (2009-2011)}{Jul 2009 - Jun 2012}
      \resumeItemListStart
        \resumeItemSimple
          {Consulted for clients [at a top 50 global consulting firm...] in the sales and marketing space, specializing in analytics and quant market research}
        \resumeItemSimple
          {Led the team evaluating the impact of competitor entry on a \$4.5Bn brand facing patent expiration; Conducted a global market research study and modeled product share using statistical conjoint analysis}
        \resumeItemSimple
          {Collaborated with ZS academic experts to develop an innovative choice modeling solution that returned quantitative, data-driven recommendations on the relative weight of customer preferences}
        \resumeItemSimple
          {Firm Leadership: Created and led firm-wide trainings on quantitative research methods, statistical modeling, and PowerPoint design as an instructor for ‘ZS University’}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------Independent Coursework-----------------
\section{Independent Coursework}
  \resumeSubHeadingListStart
    \resumeSubItemSimple
      {UCSD Coursera - Data Structures and Algorithms Specialization $\sbullet$ Stanford CS106b - Programming Abstractions Harvard CS50 - Introduction to Computer Science $\sbullet$ UC Berkeley CS162 - Operating Systems and Systems Programming $\sbullet$ Stanford CS144 - Introduction to Computer Networking $\sbullet$ Stanford Lagunita - Introduction to Databases $\sbullet$ AWS Developer edX - Building on AWS}
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{PathSchedule}
      {Developed an Amazon Alexa skill using AWS Lambda, Node.js, and GTFS transit data to respond to queries about upcoming PATH train times}
  \resumeSubHeadingListEnd


%--------Volunteering and Interests------------
% \section{Volunteering and Interests}
%  \resumeSubHeadingListStart
%     \resumeSubItem{Volunteering}
%       {Taught 4th graders engineering and robotics concepts using Lego Mindstorms as a member of NYCares}
%     \resumeSubItem{Interests}
%       {City captain for Tea With Strangers, hiking, technology, wearables, scuba diving, social psychology}
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}